Arc Blanc: a real time ocean simulation framework

### 2025-02-04 paper.tex
Clarify implementation details

Second, as \framework simulates a tile of water of size $N\times N$ using $c$ cascades, it stores the height, the displacement and so on in an 1D array of size $c$ containing a vector of 2D arrays of size $N\times N$.

>>>>

Second, as \framework simulates a tile of water of size $N\times N$ using $c$ cascades, it stores the height, the displacement, and other relevant data in a 1D array of size $c$, where each entry contains a vector of 2D arrays of size $N\times N$. \Framework compute efficiently these values on the GPU, with dedicated kernel that are launched with a grid of threads structured as $N \times N \times c$. Specifically, $N \times N$ threads are assigned to the $x$ and $y$ dimensions to cover the spatial resolution of the water tile, while $c$ threads along the $z$ dimension correspond to the different cascades. This approach ensures that computations for all cascades are executed in parallel.
